Optimal (Multiway) Spatial Joins

### 2024-05-31 msj.tex
yufei

>>>>

Next, we consider the find-all-sorted version of Problem $\mathscr{D}$. Again, initialize an array $A$ of size $|R|$, where each rectangle of $R$ is allocated a cell. For each $r \in R$, we keep a linked list, which at the end of our algorithm will store the horizontal segments of $\cross_H(r)$ in ascending order of their y-coordinates. A pointer referencing the linked list is stored in the array cell of $r$. In the outset, all the linked lists are empty. Unlike the detection version, we do not need to record whether a rectangle is active or not.

Again, sweep a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. The rectangle $r$ will be referred to as the {\em host} of $[x_1, x_2]$ and is stored together with $[x_1, x_2]$ in $\T$.

When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a containment query on $\T$ to find all the intervals in $S_\ell$ that are contained by $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain its host rectangle $r$. It is clear that $h$ is a segment crossing $r$ and is thus appended to the linked list of $r$. Note that $h$ is higher than all the segments already existing in that linked list.
